Title here

### 2016-09-14 portfolio/text/ms.Rmd
Correct season length definition

\noindent
where $s$ indexes species from $1$ through $n$.
We calculated effort or effective season length as
the sum of days fished across each permit each year.
For example, if someone fished for 30 days
on a salmon drift gillnet permit in Southeast Alaska
and 40 days on a statewide longline halibut permit,
that individual's season length
would be 70 days.

@@

The basic model is a hierarchical linear regression with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time $t$:

>>>>

\noindent
where $s$ indexes species from $1$ through $n$.
We calculated effort or effective season length as
the sum the season lengths for each permit each year.
Season length for a given permit 
was calculated as the the number of days between 
the first instance of fishing a permit 
and the last instance of fishing a permit each year.
For example, if someone fished for 30 days
on a salmon drift gillnet permit in Southeast Alaska
and 40 days on a statewide longline halibut permit,
that individual's season length
would be 70 days.

@@

The basic form of our model was a 
hierarchical linear regression with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time $t$:
